---
title: "Trust review of LOS, 2018 - 2019"
output:
  html_document:
    css: styles(Activity_6_complete).css
    #theme: united
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include =FALSE}
library(NHSRdatasets)
data("LOS_model")
```

***

####  Background of report

<section>

<span>
  The report ahead outlines some key statistics involved in the Length of Stay metric on a national basis.    
  The table you see next is a simple summary of key findings from that this dataset.  
</span> 
  
```{r, include =TRUE, echo=FALSE}
  LOS_summary <- within(LOS_model, rm(ID,Organisation)) 
  summary(LOS_summary)
```

</section>
*** 

#### Preview of the data style (what the headings mean)


<section>

<span>
Key metric analysis include the following headline figures -
</span>

```{r, include =TRUE, echo=FALSE, warning=FALSE}
  library(kableExtra)
  dt <- LOS_model 
  head(dt) %>% 
    kable() %>% 
    kable_styling(bootstrap_options = "striped", full_width = F)
    
```

##### Explaining the table
  
<body class="listformat">
- The ID is a unique numeric identifier for a trust (unique only to this table)
- For the purposes of anonymity, trust names are simply listed as 'Trust1', 'Trust2' etc.
- Age of the patient (in years)
- LOS (Length of Stay) for a patient, in days
- A binary value for whether a patient lived or died in that spell ( 0 for lived, 1 for died)
</body>

</section>

***

#### Closing report remarks 

<!-- Activity 6 - Add in a figure of your choice in this section (feel free to use the one with the hospital bed shown) -->


<section>

<span>



There are several benefits to improving the metrics around Length of Stay and some of these case studies can be found in many places across the Internet.  

For one example, please click here - <a href = https://improvement.nhs.uk/documents/2898/Guide_to_reducing_long_hospital_stays_FINAL_v2.pdf> NHS Improvement Guide for reducing LOS </a>

<figure>
  <p><img src= "hospital_bed.jpeg"
  width= 50% height=50%
  class = "center"
    alt="Hospital bed">
  <figcaption> As of September 2019, the average length of stay in England's NHS hospitals is 4.52 days </figcaption>
</figure>



</span>

</section>

***

</body> 




