---
title: "Exercise B: RMarkdown Changing Text"
author: "Chris Mainey"
date: "14/01/2020"
output: html_document
params:
  Trust: "Trust1"
  Text_if_lower : "shorter than average"
  Text_if_more : "longer than average"
  extended : 0
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## `r if(params$extended == 1){"Extended"}` Length of Stay Report: `r params$Trust`

This exercise is used to develop a sample report using the `LOS_model` dataset from the `NHSRdatasets` package.
More information about this package is avaialble at:  [here](https://cran.r-project.org/web/packages/NHSRdatasets/index.html).

```{r load, echo = FALSE}
library(NHSRdatasets)
data(LOS_model)
```

## Full dataset statistics

Here is a summary of the LOS using `dplyr`, collapsing the results into a single piece of code, with warnings surpressed, and using `knitr::kable` on the table to format it nicely. 

```{r summary, collapse=TRUE, message=FALSE}
library(dplyr)
LOS_model %>%
  summarise("Mean LOS" = mean(LOS),
            "Median LOS" = median(LOS))  %>%
  knitr::kable(caption = "LOS_model summary data for all organisations")
```

Now we will create a histogram of the LOS stay:

```{r LOS_all_plot, message=FALSE, fig.retina=2}
library(ggplot2)
ggplot(LOS_model, aes(x=LOS)) +
  geom_histogram(fill="dodgerblue2", alpha=0.6, col=1, bins=12) +
  labs(title = "Length of Stay for all patients in `LOS_models`") +
  scale_x_continuous(name="Length-of-Stay (LOS)")+
  scale_y_continuous(name="Patients")
```

<br><br>
  
***
  
<br><br>
  
## Report For `r params$Trust`
 
It is possible to change the in-line text using parameters. The title of this section of the report takes the value of the Trust parameter because it is contained inside \` \` marks.
 
We will use the same code from above, but using `filter` to return the data for the organisation named in the parameter 'Trust'.

```{r summary_trust1, collapse=TRUE, message=FALSE}
LOS_model %>%
  filter(Organisation == params$Trust) %>%
  summarise("Mean LOS" = mean(LOS),
            "Median LOS" = median(LOS))  %>%
  knitr::kable(caption = paste("LOS_model summary data for", params$Trust))
```

Here I've used the subset function rather than filter, as its another way to do the same thing and is marginally quicker than filter.

```{r LOS_trust1_plot, message=FALSE, fig.retina=2}
ggplot(subset(LOS_model, Organisation==params$Trust), aes(x=LOS)) +
  geom_histogram(fill="dodgerblue2", alpha=0.6, col=1, bins=12) +
  labs(title = paste("Length of Stay for all patients at",  params$Trust, "in `LOS_models`")) +
  scale_x_continuous(name="Length-of-Stay (LOS)")+
  scale_y_continuous(name="Patients")
```

Use the parameters 'Text_if_lower' and 'Text_if_more' to complete the following sentence.

```{r find_means, echo = FALSE}
All_LOS_mean <- mean(LOS_model$LOS)
trust_LOS_mean <- mean(LOS_model[which(LOS_model["Organisation"] == params$Trust), "LOS"])
```

`r params$Trust` has a length of stay which is `r if(trust_LOS_mean < All_LOS_mean){params$Text_if_lower} else {params$Text_if_more}`.

`r if(params$extended == 1){"### Deaths vs Age"} `

```{r death_age_plot, echo=FALSE}

if(params$extended == 0){
  # no change
} else {

LOS_model <- LOS_model %>%
  mutate(age_category = case_when(
    Age < 17 ~ "0-16",
    Age < 65 ~ "17-64",
    TRUE ~ "65+"
    ))



ggplot(LOS_model %>% filter(Organisation == params$Trust & Death == 1), aes(x=age_category)) +
  geom_bar() +
  scale_y_continuous(name = "Deaths") +
  scale_x_discrete(name = "Age")
}
```

