---
title: 'Exercise 11: RMarkdown Batches'
author: "Chris Mainey"
date: "14/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The RMarkdown file in the previous exercise used a parameter in its YAML header in order to select data for 'Trust1'. We could change this value and then press 'Knit' each time that we wanted to make a report for a different trust, but if there are 200 trusts this would take a very long time.

Instead of doing this manually, we can change the parameter and create the report using the `render` function of rmarkdown.

`render` is called as part of the 'knit' process and takes its function arguments from the YAML header by default. If arguments are given to the function they will _override_ the YAML header values, including the `params` variable. `render` can be used to customise the output file name, input parameters, and many other important features.

Create a `for` loop to write a report for every trust in the `LOS_model` dataset:

```{r Rmarkdown_batch echo = TRUE, eval=FALSE}
# Load the data set
library(NHSRdatasets)
data(LOS_model)

# Make a list of trusts to build reports for
trusts <- levels(LOS_model$Organisation)

# Make a folder to keep the files in
if(!dir.exists("report_batch")){
  dir.create("report_batch")
}

# for loop to write the reports with the render function
for(trust_name in trusts){
  
  # render can take a lot of parameters. For this exercise we have used:
  #     input is the .Rmd file to build a report from. Use your own file or the one in Exercises/Solutions/
  #     output_file is the name of the file which will be created. Make sure it is different for each loop, or it will overwrite the existing file each time
  #     params is a LIST of named variables to pass to the report. The solution report has the variable Trust = "Trust1"
      
  rmarkdown::render(input = "Ex10_RMarkdown_Report.Rmd"
                    , output_file = file.path("report_batch"
                                              , paste("Ex10_report_"
                                                      , trust_name
                                                      , sep = ""
                                                      )
                                              )
                    , params = list(Trust = trust_name)
  )
}
```