---
title: 'Exercise 3: Kable Tables'
author: "Matthew Bass"
date: "20/02/2020"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Exercise

This exercise is used to develop a sample report using the `LOS_model` dataset from the `NHSRdatasets` package.
More information about this package is avaialble [here](https://cran.r-project.org/web/packages/NHSRdatasets/index.html).

```{r load, echo = FALSE, message=FALSE, warning=FALSE}
# Load the data set here
library(NHSRdatasets)
library(dplyr)
library(kableExtra)
data(LOS_model)
```

## Full dataset

Here is the full LOS_model dataset printed with kable.

```{r}
kable(LOS_model) %>%
  kable_styling()
```


## Full dataset statistics

Here is a summary of the LOS using `dplyr`. It uses Kable to make the table look a bit nicer.

```{r summary, message=FALSE}

summary_data <- LOS_model %>%
              summarise("Mean LOS" = mean(LOS),
                        "Median LOS" = median(LOS))

kable(summary_data) %>%
  kable_styling()
```

Now we will create a histogram of the LOS stay:

```{r LOS_all_plot, message=FALSE, fig.retina=2}
library(ggplot2)
ggplot(LOS_model, aes(x=LOS)) +
  geom_histogram(fill="dodgerblue2", alpha=0.6, col=1, bins=12) +
  labs(title = "Length of Stay for all patients in `LOS_models`") +
  scale_x_continuous(name="Length-of-Stay (LOS)")+
  scale_y_continuous(name="Patients")
```

