---
title: "Activity 1"
output:
  html_document:
    css: styles(Activity_4_complete).css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Activity 4 : Switch some of the code below so that it uses a combination of traditional Markdown as well as HTML.  The first heading has been changed for you, as has the evolution of the 'span' tag, replacing 'p' tags -->

```{r, include =FALSE}
library(NHSRdatasets)
data("LOS_model")
```

***

####  Background of report

<section>

<span>
  The report ahead outlines some key statistics involved in the Length of Stay metric on a national basis.    
  The table you see next is a simple summary of key findings from that this dataset.  
</span> 
  
```{r, include =TRUE, echo=FALSE}
  LOS_summary <- within(LOS_model, rm(ID,Organisation)) 
  summary(LOS_summary)
```

</section>
*** 

#### Other views of the summary of data

<section>

<span>
Key metric analysis include the following headline figures -
</span>
  
<body class="listformat">
- Your text to go here
- Your text to go here
- Your text to go here
- Your text to go here
- Your text to go here
</body>

</section>

***

#### Closing report remarks 

<section>

Your text to go here 

</section>

***

</body> 




