---
title: "Activity 7"
output:
  html_document:
    
    css: "styles(Ex_7).css"
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Activity 7 : Switch some of the code below so that it uses a combination of traditional Markdown as well as HTML.  The first heading has been changed for you, as has the evolution of the 'span' tag, replacing 'p' tags -->

```{r, include =FALSE}
library(NHSRdatasets)
data("LOS_model")
```

***

####  Background of report

<span>
The report ahead outlines some key statistics involved in the Length of Stay metric on a national basis.    
The table you see next is a simple summary of key findings from that this dataset.  
</span>


```{r, include =TRUE}
LOS_summary <- within(LOS_model, rm(ID,Organisation)) 
summary(LOS_summary)
```

*** 

<h4> Other views of the summary of data </h4>

<span>
Key metric analysis include the following headline figures -
</span>




 Your text to go here  
 Your text to go here   
 Your text to go here  
 Your text to go here  
 Your text to go here  


***

<h4> Closing report remarks </h4>



***

</body> 




