---
title: "Trust review of LOS, 2018 - 2019"
output:
  html_document:
    #css: styles(Activity_4_complete).css
    theme: sandstone
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include =FALSE}
library(NHSRdatasets)
data("LOS_model")
```

***

####  Background of report

<section>

<span>
  The report ahead outlines some key statistics involved in the Length of Stay metric on a national basis.    
  The table you see next is a simple summary of key findings from that this dataset.  
</span> 
  
```{r, include =TRUE, echo=FALSE}
  LOS_summary <- within(LOS_model, rm(ID,Organisation)) 
  summary(LOS_summary)
```

</section>
*** 

#### Preview of the data style (what the headings mean)



<section>

<span>
Key metric analysis include the following headline figures -
</span>


<!-- Activity 5 - Add in a 'kable' method below of displaying a section of data from the table of your choice -->

```{r, include =TRUE, echo=FALSE, warning=FALSE}
  library(kableExtra)

    
```

##### Explaining the table


<body class="listformat">
- Your text to go here  
- Your text to go here  
- Your text to go here  
- Your text to go here  
- Your text to go here  
</body>

</section>

***

#### Closing report remarks 

<section>

Your text to go here 

</section>

***

</body> 




